opponent modelling

### 2019-11-08 comp_model_1019.Rmd
added parametric EWA

## Q-learning with state space including last actions

>>>>

## Parametric EWA

indicator <- function(strat,action)
  if (strat == action) { 
    return (1)
  else

EWA_par <- function(par,data,return_value=c("-2loglik","likelihood_by_trial")){
  # actions
  # beta= inverse temperature parameter in softmax choice function
  # lambda = learning rate (one per game?)
  # data : participant and ai choice data.
  # Returns Q-values per trial and predicts choice using softmax
  phi <- par[1]
  delta <- par[2]
  kappa <- par[3]
  lambda <- par[4]

  N <- 1

  A_RPS = matrix(0.0,3)
  names(A_RPS) <- c("R","P","S")
  A_FWG = matrix(0.0,3)
  names(A_FWG) <- c("F","W","G")
  A_NUM = matrix(0.0,5)
  names(A_NUM) <- c("1","2","3","4","5")

  for(t in 1:nrow(data)) {
    t_game <- data[t,"game"]
    if(t_game == "numbers") nopts <- 5 else nopts <- 3
    if(data[t,"round"] == 1) {
      # first round is uniform prediction
      Att <- switch(as.character(t_game),rps=A_RPS,fwg = A_FWG, numbers = A_NUM)
      lik_hum[t] <- 1/nopts
    } else {
      # Get reward and past human action
      reward <- as.numeric(data[t-1,"score"])
      h_act_prev <- as.character(data[t-1,"h_action"])

      Att[h_act_prev] <- (phi*N*Att[[h_act_prev]]  + reward

      # Get actual human action and compute likelihood
      h_act <- as.character(data[t,"h_action"])
      act_index <- match(h_act, names(Q_vals))
      lik_hum[t] <- probs[[act_index]]
    }
  }
